### 2019-08-22 Writeup/Thesis/chapters/design.tex
Changes; - More progress added to the thesis

\section{Overall attack design}

@@

    \item Calculate all permutations of near-collisions for the key pair and produce a list of similar key fingerprints.

    \item Use a list of similar keys in the mass computation of keys to find near-collision keys.

@@

\subsubsection{Matches}
A match for each code based metric (Soundex, Metaphone and NYSIIS) occurs when the codes are identical. However, for the other cases where the difference is variable other ways of defining a match are required.

@@

As it can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex. As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundexIssues}) it can be excluded as an abnormality in this context. Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.

@@

\subsubsection{Comparisons}
Each participant is asked to rate the similarity of a match on a scale of 1 to 5. Figure \ref{fig:phoneticMatch} shows an example match and the connected scale. Users are provided with five of these comparisons per metric.

@@

The final experiment required to answer Research Question \ref{goal:attackPercentage} requires the simulation attacks on participants. The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).

@@

Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but it is a balance between resources and realistic design. Alongside, this the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are lulled into a level of complacency regarding the possibility of an attack.

Certain keys have higher levels of near-collision possibilities than others due to how certain words are deemed similar by the chosen metric. Therefore, this presents the possibility to have keys with a very low number of similar matches. The distribution of these keys is explained further in Chapter \ref{cha:Experiments}. Therefore, if random sets of words are chosen with no restraints, there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits). Therefore, the experiment is designed to sample from a list of "vulnerable" keys. These are keys that have a number of combinations that allow an attack in a specified timeframe.

Furthermore, certain levels of attacks are also simulated. Below is the list of possible attacks:

\begin{itemize}
    \item \textbf{Zero static words} - All words in the set can vary.
    \item \textbf{One static word} - All but the first word can vary.
    \item \textbf{Two static words} - All but the first and last word can vary.
\end{itemize}

@@

These attacks are ascending in complexity. The timeframe for finding a match was decided as 7-days with attack strengths of 1 GPU/day, 10 GPU/days and 100 GPU/days on a mid-range GPU (AMD RX 480 was the example in experiments). Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack. The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys. This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More combinations make the attack search quicker. Any key that exceeds this criterion is deemed as vulnerable. A list of these vulnerable keys is sampled from when an attack is simulated. The percentage of vulnerable keys is explored in Chapter \ref{cha:Experiments}.

@@

Overall-time is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses. Anything below a certain threshold is discarded.

>>>>

\section{Overall attack design}
\label{sec:attackDesign}

@@

    \item Calculate all permutations of near-collisions for the key pair and produce a list of near-collision key fingerprints.

    \item Use a list of near-collision keys in the mass computation of keys to find near-collision keys.

@@

\subsubsection{Matches}
\label{sec:matches}

A match for each code based metric (Soundex, Metaphone and NYSIIS) occurs when the codes are identical. However, for the other cases where the difference is variable other ways of defining a match are required.

@@

As it can be seen from Table \ref{tab:matchSize}, the number of matches for L2 is more significant than all metrics excluding Soundex. As the issues with Soundex have been discussed in previous sections (See Section \ref{sec:soundex}) it can be excluded as an abnormality in this context. Therefore, due to the excessively high value for a L2, L1 was chosen as the Levenshtein cap for defining a match.

@@

\subsubsection{Comparisons}
Each comparison contains a match-pair. These matches are generated by running the similarity metric over all the pairings in the Trustword dictionary, if the pair meets the criteria discussed in the previous section it is determined a match. Potential matches are then sampled from their respective lists.

Each participant is then asked to rate the similarity of a match on a scale of 1 (\textit{`Very different sound'}) and 5 (\textit{`Very similar sound'}). Figure \ref{fig:phoneticMatch} shows an example match and the connected scale. Users are provided with five of these comparisons per similarity metric.

@@

This experiment is designed to be a simulation of the attack proposed in Section \ref{sec:attackDesign}, in an attempt to answer Research Question \ref{goal:attackPercentage}. The experiment will test the simulated matches of three similarity metrics decided by the previous experiment (See Section \ref{sec:metrics}). The overall aim of the experiment is to quantify the success rate of the attack on live participants. The user is presented with the same design as the \pep Android application (See Section \ref{sec:pep}).

@@

Due to the scarcity of attacks in a real-world setting, users are often complacent about their occurrence. Therefore, in this experiment, attacks only occur 30\% of the time. This occurrence is a much higher value than in a real-world setting, but is a balance between resources and realistic design. If the chosen attack rate is too low, many more trials are required to collate a useful number of attack instances, thus, requiring more resources but with a much more realistic design. If, however, the attack rate is too high, less total rounds are required to obtain the target number of attack trails, however, the user will lose their complacency as an attack will be expected. This loss of complacency is undesirable as it does not realistically reflect real life. Furthermore, the first 5 trials of a new experiment is always benign. This inclusion is to ensure users are consistently lulled into of complacency.

Certain keys have higher levels of potential near-collision keys than others due to how certain words are deemed similar by the similarity metric. Therefore, this presents the possibility to have keys with a very low number of possible near-collision keys. The distribution of these keys is explained further in Chapter \ref{cha:Experiments}. Therefore, if random sets of words are chosen with no restraints, there are attacks presented to the user that in a real setting would be infeasible as they are close to a $2^{64}$ attack (4 Words * 16-bits). Therefore, the experiment is designed to sample from a list of "vulnerable" keys. These are keys that have a number of potential near-collision keys that allow computation in a specified timeframe.

Furthermore, certain levels of attacks are also simulated. Below is the list of attacks considered in this experiment:

\begin{itemize}
    \item (\OOOO) All words in the set can vary             
    \item (\XOOO) All but the first word can vary           
    \item (\XOOX) All but the first and last word can vary  
\end{itemize}

$Where: $
\begin{itemize}
    \item[] \verb|X|: is a static word
    \item[] \verb|O|: is a changeable word
\end{itemize}

@@

These attacks are ascending in complexity. The timeframe for computing a near-collision was decided as 7-days with attack strengths of 1 GPU-day, 10 GPU-days and 100 GPU-days on a mid-range GPU (AMD RX 480). Due to the long lifetime of PGP keys, 7 days was chosen as a reasonable length of the attack. The tool requires no user interaction once started, therefore, it can be left for an extended period to compute potential keys. This timeframe is also a maximum time, these attacks also include keys that have a shorter average computation time.

@@

Table \ref{tab:attackReq} contains a summary of the different level of attacks and their respective restrictions. More potential near-collision keys make the attack search quicker. Any key that exceeds the defined numbers of potential near-collision key for attack level are deemed as vulnerable.  As discussed in Section \ref{sec:attackDesign} the near-collision keys are close keys produced from the similarity-metric's matches. A list of these vulnerable keys is sampled from when an attack is simulated. The percentage of vulnerable keys is explored in Chapter \ref{cha:Experiments}.

@@

Overall-time is as the name suggest a recording of the time taken to complete the entire experiment. If users complete the experiment in an abnormally small amount of time, it can be used as another detection for invalid responses. A benchmark for the time is set by completing the experiment correctly but as fast as possible. Anything below this pace was discarded as anything higher will risk invalid and rushed results.

### 2019-08-22 Writeup/Thesis/chapters/implementation.tex
Changes; - Added some changes from supervisor - Began fixing structure of the document
Changes; - More progress added to the thesis

\begin{figure}[!h]
  \centering
  \input{diagrams/code/OpenKernel.tex}
  \caption{OpenCL Kernel}
  \label{fig:opencl}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \input{diagrams/code/ExponentIncrement.tex}
  \caption{Exponent incrementation code}
  \label{fig:increment}
\end{figure}

@@

\section{First Experiment}
In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided the functionality to present questions easily and record responses. However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality, an extra solution was required. This problem was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to interact with the Form programmatically. This addition allowed the re-sampling of matches each time a user submitted a response.

\begin{figure}[!h]
  \centering
  \input{diagrams/code/GoogleAppScript.tex}
\caption{Section of code from the First Experiment's Google App Script}
\label{fig:GoogleAppScript}
\end{figure}

>>>>

\begin{figure}[!h]
  \centering
  \input{code/OpenKernel.tex}
  \caption{OpenCL Kernel}
  \label{fig:opencl}
\end{figure}

@@

\begin{figure}[!h]
  \centering
  \input{code/ExponentIncrement.tex}
  \caption{Exponent incrementation code}
  \label{fig:increment}
\end{figure}

@@

\section{First Experiment}
As discussed in Section \ref{sec:matches} as list of matches were generated by each metric. Figure REF shows the algorithm designed to compute these match lists. It loads the Trustword dictionary and works through all combinations of matches.

\begin{figure}[h!]
\begin{lstlisting}[language=C++, frame=single]
  void find_similar_words(std::vector<std::string> words)
  {
      std::vector<std::string> sim_words;

      for (std::string word_y : words)
      {
          sim_words.push_back(word_y);

          for (std::string word_x : words)
          {
                // Makes sure the same words aren't checked
              if (word_y != word_x)
              {
                  bool add_word = false;

                  else
                  {
                      if (LEVENSHTEIN) add_word = 
                            leven_similar(word_y, word_x);

                      else if (METAPHONE) add_word = 
                            metaphone_similar(word_y, word_x);

                      else if (NYSIIS) add_word = 
                            nysiis_similar(word_y, word_x);
                  }

                  if (add_word)
                  {
                      sim_words.push_back(word_x);
                      add_word = false;
                  }
              }
          }
      }
  }
  \end{lstlisting}
  \caption{}
\end{figure}

Figure REF also shows an example matching algorithm for Levenshtein. The difference is computed and compared to the tolerance discussed in Section \ref{sec:matches}.

\begin{figure}[h!]
\begin{lstlisting}[language=C++, frame=single]
bool leven_similar(std::string word1, std::string word2)
{
  int diff = lev_distance(word1, word2);
  return diff <= DIFFERENCE_TOLERANCE;
}
\end{lstlisting}
\caption{}
\end{figure}

In order to assess and collect data from users for the first experiment (See Section \ref{exp:metric}), Google Forms\footnote{\url{https://www.google.com/forms}} was used to host and design the questionnaire. It provided the functionality to present questions easily and record responses. However, as the design requirement of refreshing questions after each submission was not part of the main applications functionality, an extra solution was required. This problem was solved by Google's App Script\footnote{\url{https://developers.google.com/apps-script/}} service that allows a user to interact with the Form programmatically. This addition allowed the re-sampling of matches  each time a user submitted a response.

\begin{figure}[!h]
  \centering
  \input{code/GoogleAppScript.tex}
\caption{Section of code from the First Experiment's Google App Script}
\label{fig:GoogleAppScript}
\end{figure}
